Case Study (McKenna)

### 2020-04-24 Code/mrp/Case Study (McKenna) .Rmd
Cleaning up the case study to make it easier to follow.

For this first iteration of modeling, we will be generating our own data. We will generate a population, and sample from it in order to build an MRP model.

@@

@@

@@

sample <- read_csv(here("code", "mrp", "data", "sample.csv"))
proststrat <- read_csv(here("code", "mrp", "data", "poststrat.csv"))
true_popn <- read_csv(here("code", "mrp", "data", "true_popn.csv"))

```
```{r}
stan_data <- list( 
  N = nrow(sample), 
  service_failure = sample$service_failure,
  male = sample$male, 
  age = sample$age,
  eth = sample$eth, 
  income = sample$income, 
  state = sample$state)
```

@@

We now have need for a logistic regresson model in order to predict a binary outcome for 'service_failure' so we will make a hierarchal logit model

@@

@@

>>>>

For this first iteration of modeling, we will be generating our own data. We will generate a population, and sample from it in order to build an MRP model. The function will also generate an MRP table to use later to poststratify.

@@

We include the function here just for reference. The outputs have been previously saved out as "sample", "postrat", and "true_popn".

@@

Here we will import our data generated by the function.

@@

sample <- read_csv(here:here("code", "mrp", "data", "sample.csv"))
proststrat <- read_csv(here:here("code", "mrp", "data", "poststrat.csv"))
true_popn <- read_csv(here:here("code", "mrp", "data", "true_popn.csv"))

```
We now have need for a logistic regresson model in order to predict a binary outcome for 'service_failure' so we will make a hierarchal logit model

In this section we are working througha couple different model versions heading to the hierarichal model.

Here we are looking at running a simple logit model.

```{r}
stan_data <- list( 
  N = nrow(sample), 
  service_failure = sample$service_failure,
  male = sample$male, 
  age = sample$age,
  eth = sample$eth, 
  income = sample$income, 
  state = sample$state)
```

@@

@@

This is me thinking about what format we want the data in.

@@

Here we are trying to do a higherarical logit.
